Article data analysis

### 2019-01-25 notebooks/article_notebook.Rmd
minor changes
minor changes, added figures to article notebooks

@@

mechanism_per_species <- total_df %>%
  select(-c(gyrA, gyrB, parC, parE)) %>%
  left_join(cols_to_add, by = "id") %>%
  select(id, species, everything()) %>%
  select(-id) %>%
  gather(key, value, -species) %>%
  group_by_all() %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

@@

@@

```{r}
# alignment <- Biostrings::readAAMultipleAlignment("../data/alignment.fasta")
# msaR::msaR(alignment)
```

>>>>

total_df <- acquired_report %>%
  left_join(mut_quant[c("gyrA","gyrB","parC","parE","id")], by = "id") %>%
  left_join(mut_report[c("id","marR","marA","rpoB")], by = "id") %>%
  left_join(isolate_data[c("id", "species")])

@@

mechanism_per_species <- total_df %>%
  select(-c(gyrA, gyrB, parC, parE)) %>%
  left_join(cols_to_add, by = "id") %>%
  select(id, species, everything()) %>%
  select(-id) %>%
  gather(key, value, -species) %>%
  group_by_all() %>%
  dplyr::count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

@@

test <- hclust(daisy(cgMLSTdata, metric="gower"))

@@

```{r}
alignment <- Biostrings::readAAMultipleAlignment("../data/alignment.fasta")
msaR::msaR(alignment)
```
